The Unified Nature of the Dielectric Properties of Two-Dimensional Materials

### 2018-11-12 paper.tex
Change section 2

% \section{Introduction}
% \label{sec:org2ea169d}
\linenumbers{}

@@

$\alpha^{\perp}$ is directly related with the intrinsic thickness of
2D materials. We further introduce the concept of dielectric
anisotropy index, to unify 2D and 3D dielectric property. The proposed
universal dielectric scaling relationships of 2D compounds introduce a
general pathway for the exploration of their complex physical and
chemical phenomena well beyond the currently possible applications.

@@

In persuit of the Moss-like relation of 2D materials, an accurate
description of the dielectric properties of 2D materials needs to be
established. One challenge is that the concept of macroscopic
dielectric constant is ill-defined for 2D materials

@@

tensor from the superlattice $\varepsilon_{\mathrm{SL}}$, is

@@

polarization density $\boldsymbol{P}^{p}$, under small
perturbative external field $\boldsymbol{E}^{q}$, where $p$, $q$ are
the directions in $(x, y, z)$, such that:

@@

    &\varepsilon^{p} &= \kappa^{pq} +

@@

$\boldsymbol{u}$ is the total dipole moments of the SL, $\rho$ is the
spatial charge density, $\Omega=AL$ is the volume, $A$ is the xy-plane
area of the SL and $\varepsilon_{0}$ is vacuum permittivity. For the
majority of 2D semiconductors, the off-diagonal elements of the
dielectric tensor ($p \neq q$) tend to be negligible.  Considering
that the 2D material is placed in vacuum, such that $\kappa^{pp} = 1$
and $\kappa^{pq} = 0$, we can distinguish two components of the SL
dielectric tensor, namely the in-plane

@@

\varepsilon_{\mathrm{SL}}^{zz}$. Due to the absence of bonding along
the z-direction, the induced charge density of a 2D material is highly
confined in the xy-plane but delocalised along of the
z-direction. Figure \ref{fig-1}a shows the charge density difference

@@

$|\boldsymbol{E}_{z}|=0.01 \mathrm{V\cdot \AA}^{-1}$, which extends to
$\sim{}$12 \AA{} along the z-direction. When $L$ is large enough, the
induced dipoles from periodic images do not overlap, and the total
dipole moments $\boldsymbol{u}$ of the SL in Eq. \ref{eq:def-eps-2} is
independent of $L$. As a consequence, we can see from
Eqs. \ref{eq:def-eps-1} and \ref{eq:def-eps-2}, that both

@@

respectively. We observe that neither
$\varepsilon^{\parallel}_{\mathrm{SL}}$ nor
$\varepsilon^{\perp}_{\mathrm{SL}}$ converges with $L$ due to fact
that the long-range Coulomb interaction could not be completed
screened within the range of magnitudes computationally accessible
\cite{Hueser_2013_2Dvs3D}. The $L$-dependency of macroscopic
dielectric constant makes it erroneous to use
$\varepsilon_{\mathrm{SL}}$ to represent the dielectric nature of a 2D
material. Therefore, we need to find a $L$-independent quantity to
present the intrinsic dielectric properties of the 2D materials. As
discussed previously, since the total dipole moments $\mathbf{u}$
remain constant with $L$, we can define the surface or sheet
polarization density matrix $\boldsymbol{\mu}$, by multiplying
Eq. \ref{eq:def-eps-2} with $L$, such that
$\boldsymbol{\mu}^{p} = \boldsymbol{P}^{p}L = \int_{\mathrm{SL}}
\rho(\boldsymbol{r}) \boldsymbol{r}^{p}d^{3} \boldsymbol{r}/A$, which
is independent of the superlattice size. Similar to the definition of
molecular polarizability \cite{Israelachvili_2011}, the sheet
polarization density $\boldsymbol{\mu}$ is associated with the 2D
polarizability tensor $\alpha$ through:
$\boldsymbol{\mu}^{p} = \sum_{q} \alpha^{pq}
\mathbf{E}_{\mathrm{loc}}^{q}$ \cite{T_bik_2004}, where
$E_{\mathrm{loc}}$ is the local electric field. In the in-plane
direction, the continuity of electric field gives
$\mathbf{E}^{\parallel}_{\mathrm{loc}}=\mathbf{E}^{\parallel}$

@@

$\boldsymbol{E}_{\mathrm{loc}}^{\perp}=\boldsymbol{E}^{\perp}+\boldsymbol{\mu}^{\perp}/L$

@@

$\alpha^{\parallel}$ and $\alpha^{\perp}$, respectively:

@@

  &\alpha^{\parallel} &= \varepsilon_{0}(\varepsilon_{\mathrm{SL}}^{\parallel} - 1)L\\

@@

    &\alpha^{\perp} &= \varepsilon_{0}\left(1 - {\displaystyle \frac{1}{\varepsilon_{\mathrm{SL}}^{\perp}}}\right)L

@@

$\alpha^{\parallel}$ and $\alpha^{\perp}$ of the TMDCs as functions of
$L$, calculated using Eqs. \ref{eq:alpha-para-def} and
\ref{eq:alpha-perp-def}. We observe that both $\alpha^{\parallel}$ and
$\alpha^{\perp}$ remain almost constant when $L>$15 \AA{}. In
addition, by varying the value of $\alpha^{\parallel}$ and
$\alpha^{\perp}$, we can nicely reproduce the $L$-dependence of
$\varepsilon_{\mathrm{SL}}^{\parallel}$ and
$\varepsilon_{\mathrm{SL}}^{\perp}$ of the TMDCs, as shown Figure \ref{fig-1}d
and \ref{fig-1}e, respectively. These findings indicate that the 2D polarizability,
instead of the dielectric constant, is the true descriptor of the
dielectric properties of 2D materials.

It is also worth mentioning that the dielectric properties of 2D
materials are also often modeled using an effective medium approach,
which treats the 2D material as a slab with effective permittivity
$\varepsilon_{\mathrm{2D}}$ and thickness $\delta$
\cite{Sharma_1985,Cudazzo_2011_screening_2D,Matthes_2016,Trolle_2017_eps_subst,Laturia_2018}. Such
methods require \textit{a priori} determination of $\delta$, a
quantity with controversial definitions \cite{Mas_Ballest__2011}. In
such approaches, $\varepsilon_{\mathrm{2D}}$ and $\delta$ have to be
determined by fitting the $L$-dependent data of
$\varepsilon_{\mathrm{SL}}$, which is not only computational
expensive, but also fails to capture the anisotropy of the 2D
dielectric properties (see Supplementary Section S1). On the other
hand, calculating 2D polarizabilities requires no knowledge of
$\delta$ (see Eqs. \ref{eq:alpha-para-def} and
\ref{eq:alpha-perp-def}), and correctly presents the anisotropy of 2D
dielectric nature that $\alpha^{\parallel} > \alpha^{\perp}$.  With
the polarizability as the true descriptor of 2D dielectric properties,
we will reveal the universal Moss-like relation of 2D materials from
both theoretical and first principles studies.

@@

In this section we theoretically investigate the existence of the 2D
Moss-like relations, based on the 2D polarizability.  Due to its
highly anisotropic nature, the wavefunction of an isolated 2D material
$\psi(\mathbf{r})$ can be separated into the in- and out-of-plane
components, similar to the treatment of quantum wells
(QW),\cite{davies_physics_1997} such that
$\psi^{\parallel}(\boldsymbol{\rho})$ and $\psi^{\perp}(z)$, such that
$\psi=\psi^{\parallel}\psi^{\perp}$, where $\boldsymbol{\rho}=(x, y)$
is the in-plane coordinate. Using the Bloch theorem, the periodic
$\psi^{\parallel}(\boldsymbol{\rho})$ can be further expressed as

@@

\subsection{2D Moss Relations}
\label{sec:first-principles}
We study several types of 2D materials of different electronic and
optical properties as show in Figure \ref{fig-2}, including transition
metal dichalcogenides (TMDCs, with the formula MX\(_{\text{2}}\),
where M is a metal in group 4, 6, 10 and X=O, S, Se, Te), metal
monochalcogenides (Ga$_{2}$S$_{2}$, Ga$_{2}$Se$_{2}$), cadmium halides
(CdX$_2$, X=Cl, I), hexagonal boron nitride (BN), graphene derivatives
(fluorographene (C$_{2}$F$_{2}$), graphane (C$_{2}$H$_{2}$)),
phosphorene (P$_{4}$) and thin layer organic-inorganic perovskites
(ABX$_{3}$).  For the TMDCs, we consider 2 lattice phases, namely the
2H (P\(\bar{6}\)m2 space group) and 1T (P3m1 space group).  The static
2D polarizabilities are calculated from the static dielectric response
of the selected 2D materials using density functional theory (DFT)
with the Heyd-Scuseria-Ernzerhof hybrid functionals (HSE06) using the
Vienna Ab Initio Simulation Package (VASP) including spin-orbit
coupling to avoid limitations on the description of band gaps and
dielectric functions (see Methods for details).

@@

% \section{Figures}
\label{sec:org34cbe74}
\begin{figure}[htbp]
\centering
\includegraphics[width=0.75\linewidth]{img/fig1.pdf}
\caption{\label{fig-1} \textbf{2D polarizability as the true
    descriptor of the dielectric nature of 2D materials.}
  \textbf{a}. 3D illustration of the spatial distribution of the
  charge density change $\Delta \rho(z)$ along the z-direction for
  monolayer 2H-MoS$_{2}$ in a periodic superlattice under external
  eletric field of 0.01 V/\AA{}.  The green and red regions represent
  negative and positive induced charges, respectively. The macroscopic
  $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
  $\varepsilon_{\mathrm{SL}}^{\perp}$ are influenced by the lattice
  size $L$, while the 2D polarizabilities $\alpha^{\parallel}$ and
  $\alpha^{\perp}$ are invariant with lattice size \textbf{b}.
  $\varepsilon^{\parallel}_{\mathrm{SL}}$ (top) and
  $\alpha_{\mathrm{SL}}^{\parallel}$ (bottom) as functions of $L$ for
  the 2H TMDCs. \textbf{c}.  $\varepsilon^{\perp}_{\mathrm{SL}}$ (top)
  and $\alpha_{\mathrm{SL}}^{\perp}$ (bottom) as functions of $L$ for
  the 2H TMDCs. The polarizabilities in \textbf{b} and \textbf{c} are
  constant when $L>$15 \AA{}, compared with the $L$-dependence of
  $\varepsilon_{\mathrm{SL}}$. \textbf{d} and \textbf{e}: modeled
  $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
  $\varepsilon_{\mathrm{SL}}^{\perp}$ corresponding with \textbf{b}
  and \textbf{c}, from Eqs. \ref{eq:alpha-para-def} and
  \ref{eq:alpha-perp-def}, respectively.}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\linewidth]{./img/fig2.pdf}
\caption{\label{fig-2} The elements and 3D structures of the 2D
  materials investigated in this study.}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=0.95\linewidth]{./img/fig3.pdf}
\caption{\label{fig-3} \textbf{The universal scaling relation of the
    dielectric nature of 2D
    materials}. \textbf{a}. $\alpha^{\parallel}$, $\alpha^{\perp}$
  (bar plots) and $E_{\mathrm{g}}$ (blue dots) for all the 2D
  materials studied.  $\alpha^{\parallel}$ is observed to descend with
  increasing $E_{\mathrm{g}}$, while no apparent relation between
  $\alpha^{\perp}$ and $E_{\mathrm{g}}$ is
  observed. \textbf{b}. $(4\pi \varepsilon_{0})/\alpha^{\parallel}$
  (in \AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$, showing a linear
  correlation between each other. The energy range of visible light is
  shown in the
  background. \textbf{c}. $\alpha^{\perp}/(4\pi\varepsilon_{0})$ (in
  \AA{}) as a function of $\delta_{\mathrm{cov}}$ (definition
  schematically shown in the inset), showing a perfect linear relation
  with slope very close to $1/4\pi$. The universal scaling relation is
  also revealed using the C2DB database (squares), as superimposed on \textbf{b}
  and \textbf{c}.}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.85\linewidth]{./img/fig4.pdf}
\caption{\label{fig-4} \textbf{Transition of dielectric properties
    from 2D to 3D systems}. \textbf{a}. Scheme for the 2D-3D
  transition. $\alpha$ in the 2D material is essentially equivalent to
  $\varepsilon$ in its bulk counterpart. \textbf{b}
  $\varepsilon_{\mathrm{bulk}}^{\parallel}$ calculated from DFT
  (y-axis) compared with the predicted value from 2D
  $\alpha^{\parallel}$ (x-axis), showing good correlation. \textbf{c}
  $\varepsilon_{\mathrm{bulk}}^{\perp}$ calculated from DFT (y-axis)
  compared with the predicted value from 2D $\alpha^{\parallel}$
  (x-axis). The predicted value is in good aggreement with the DFT
  calculation when $E_{\mathrm{g}}>4$ eV, due to minimal interlayer
  coupling. The comparisons in \textbf{b} and \textbf{c} are made
  based on both HSE06 (circles) and PBE (squares) levels.}
\end{figure}

>>>>

% \section{Introduction}
% \label{sec:org2ea169d}
% \linenumbers{}

@@

$\alpha^{\perp}$ is directly related with the thickness
$\delta$ of a 2D materials. We further introduce the concept of
dielectric anisotropy index, to unify 2D and 3D dielectric
property. The proposed universal dielectric scaling relationships of
2D compounds introduce a general pathway for the exploration of their
complex physical and chemical phenomena well beyond the currently
possible applications.

@@

In pursuit of the Moss-like relation for 2D materials, an accurate
description of their dielectric properties needs to be established,
since the concept of macroscopic dielectric constant is ill-defined
for 2D materials

@@

tensor from the superlattice $\varepsilon_{\mathrm{SL}}^{pq}$, is

@@

polarization density $\boldsymbol{P}^{p}$ under small perturbative
external field $\boldsymbol{E}^{q}$, where $p$, $q$ are the directions
of polarization and electric field,
respectively\cite{Dressel_2001_electrodynamics}:

@@

    &\varepsilon^{pq} &= \kappa^{pq} +

@@

$\boldsymbol{u} = {\displaystyle \int_{\mathrm{SL}}
  \rho(\boldsymbol{r}) \boldsymbol{r}^{p} d^{3}\boldsymbol{r}}$ is the
total dipole moments of the SL, $\rho$ is the spatial charge density,
$\Omega=AL$ is the volume, $A$ is the xy-plane area of the SL and
$\varepsilon_{0}$ is vacuum permittivity. For the majority of 2D
semiconductors, the off-diagonal elements of the dielectric tensor
($p \neq q$) tend to be negligible.  Considering that the 2D material
is placed in vacuum ($\kappa^{pp} = 1$ and $\kappa^{pq} = 0$), we can
distinguish two components, namely the in-plane

@@

\varepsilon_{\mathrm{SL}}^{zz}$. The absense of bonding perpendicular
to the 2D plane confines the induced dipoles along the
\textit{z}-direction: as shown in Figure \ref{fig-1}a and
Supplementary Figure SXX \todo{check}, the charge density difference

@@

$|\boldsymbol{E}_{z}|=0.01 \mathrm{V\cdot \AA}^{-1}$ only extends to
$\sim{}$12 \AA{} along the z-direction. When $L$ is large enough that
the induced dipoles from periodic images do not interact,
$\boldsymbol{u}$ equals the total dipole moments of a monolayer 2D
materials and independent of the SL size. As a consequence, we can see
from Eqs. \ref{eq:def-eps-1} and \ref{eq:def-eps-2}, that both

@@

respectively.
% We observe that neither
% $\varepsilon^{\parallel}_{\mathrm{SL}}$ nor
% $\varepsilon^{\perp}_{\mathrm{SL}}$ converges with $L$ due to fact
% that the long-range Coulomb interaction could not be completed
% screened within the range of magnitudes computationally accessible
% \cite{Hueser_2013_2Dvs3D}.
As a result, the $L$-dependency of $\varepsilon_{\mathrm{SL}}$ makes
it impractical to represent the dielectric nature of a 2D material
both theoretically and experimentally, because the size of vacuum
layer must always be considered. To solve this problem, we need to
find the $L$-independent alternative of
$\varepsilon_{\mathrm{SL}}$. As described before, by multiplying
Eq. \ref{eq:def-eps-2} with $L$ we get the sheet polarization density
of a 2D material $\boldsymbol{\mu}_{\mathrm{2D}}$, such that
$\boldsymbol{\mu}_{\mathrm{2D}}^{p} = \boldsymbol{P}^{p}L =
\boldsymbol{u}^{p}/A$, which is dependent with $L$ due to the invariablity
of $\boldsymbol{u}$ and $A$. Similar to the definition of molecular
polarizability \cite{Israelachvili_2011},
$\boldsymbol{\mu}_{\mathrm{2D}}$ is associated with the 2D
polarizability $\alpha_{\mathrm{2D}}$ through:
$\boldsymbol{\mu}^{p} = \sum_{q} \alpha_{\mathrm{2D}}^{pq}
\boldsymbol{E}_{\mathrm{loc}}^{q}$ \cite{T_bik_2004}, where
$\boldsymbol{E}_{\mathrm{loc}}$ is the local electric field. In the
in-plane direction, the continuity of electric field gives
$\boldsymbol{E}^{\parallel}_{\mathrm{loc}}=\boldsymbol{E}^{\parallel}$

@@

$\boldsymbol{E}_{\mathrm{loc}}^{\perp}=\boldsymbol{E}^{\perp}+\boldsymbol{\mu}_{\mathrm{2D}}^{\perp}/L$

@@

$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$, respectively:

@@

  &\alpha_{\mathrm{2D}}^{\parallel} &= \varepsilon_{0}(\varepsilon_{\mathrm{SL}}^{\parallel} - 1)L\\

@@

  &\alpha_{\mathrm{2D}}^{\perp} &= \varepsilon_{0}\left(1 - {\displaystyle \frac{1}{\varepsilon_{\mathrm{SL}}^{\perp}}}\right)L

@@

$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
of the TMDCs as functions of $L$, calculated using
Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def}. We observe
that both $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$ remain almost constant when $L>$15
\AA{}. In addition, as shown Figure \ref{fig-1}d and \ref{fig-1}e,
respectivel, the model-predicted
$\varepsilon_{\mathrm{SL}}^{\parallel}-L$ and
$\varepsilon_{\mathrm{SL}}^{\perp}-L$ relations from Eqs.
\ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def} nicely reproduce
the trends from Figures \ref{fig-1}b and \ref{fig-1}c. These findings
indicate that the 2D polarizability, instead of the dielectric
constant, is the true descriptor of the dielectric properties of 2D
materials. More discussion about the choice of the 2D polarizability
and comparison with other methods can be find in Supplementary Section
SXX \todo{xxx}.

% It is also worth mentioning that the dielectric properties of 2D
% materials are also often modeled using an effective medium approach,
% which treats the 2D material as a slab with effective permittivity
% $\varepsilon_{\mathrm{2D}}$ and thickness $\delta$
% \cite{Sharma_1985,Cudazzo_2011_screening_2D,Matthes_2016,Trolle_2017_eps_subst,Laturia_2018}. Such
% methods require \textit{a priori} determination of $\delta$, a
% quantity with controversial definitions \cite{Mas_Ballest__2011}. In
% such approaches, $\varepsilon_{\mathrm{2D}}$ and $\delta$ have to be
% determined by fitting the $L$-dependent data of
% $\varepsilon_{\mathrm{SL}}$, which is not only computational
% expensive, but also fails to capture the anisotropy of the 2D
% dielectric properties (see Supplementary Section S1). On the other
% hand, calculating 2D polarizabilities requires no knowledge of
% $\delta$ (see Eqs. \ref{eq:alpha-para-def} and
% \ref{eq:alpha-perp-def}), and correctly presents the anisotropy of 2D
% dielectric nature that $\alpha^{\parallel} > \alpha^{\perp}$.  With
% the polarizability as the true descriptor of 2D dielectric properties,
% we will reveal the universal Moss-like relation of 2D materials from
% both theoretical and first principles studies.

\iffalse

@@

\todo[inline]{In case of Nat. Nanotechnol., I would like to move all
  theoretical information to SI}.
Based on the 2D polarizability, we
then theoretically investigate the potential existence of the
Moss-like relations for 2D materials.  Due to its highly anisotropic
nature, the wavefunction of an isolated 2D material $\psi(\mathbf{r})$
can be separated into the in- and out-of-plane components, similar to
the treatment of quantum wells (QW),\cite{davies_physics_1997} such
that $\psi^{\parallel}(\boldsymbol{\rho})$ and $\psi^{\perp}(z)$, such
that $\psi=\psi^{\parallel}\psi^{\perp}$, where
$\boldsymbol{\rho}=(x, y)$ is the in-plane coordinate. Using the Bloch
theorem, the periodic $\psi^{\parallel}(\boldsymbol{\rho})$ can be
further expressed as

@@

\fi

\subsection{2D Moss Relations Based on 2D Polarizabilities}
\label{sec:first-principles}
We study several types of 2D materials of different electronic and
optical properties as show in Figure \ref{fig-2}, including transition
metal dichalcogenides (TMDCs, with the formula MX\(_{\text{2}}\),
where M is a metal in group 4, 6, 10 and X=O, S, Se, Te), metal
monochalcogenides (Ga$_{2}$S$_{2}$, Ga$_{2}$Se$_{2}$), cadmium halides
(CdX$_2$, X=Cl, I), hexagonal boron nitride (BN), graphene derivatives
(fluorographene (C$_{2}$F$_{2}$), graphane (C$_{2}$H$_{2}$)),
phosphorene (P$_{4}$) and thin layer organic-inorganic perovskites
(ABX$_{3}$).  For the TMDCs, we consider 2 lattice phases, namely the
2H (P\(\bar{6}\)m2 space group) and 1T (P3m1 space group).  The static
2D polarizabilities are calculated from the static dielectric response
of the selected 2D materials using density functional theory (DFT)
with the Heyd-Scuseria-Ernzerhof hybrid functionals (HSE06) using the
Vienna Ab Initio Simulation Package (VASP) including spin-orbit
coupling to avoid limitations on the description of band gaps and
dielectric functions (see Methods for details).

@@

% \section{Figures}
\label{sec:org34cbe74}
\begin{figure}[htbp]
\centering
\includegraphics[width=0.75\linewidth]{img/fig1_v110418i.pdf}
\caption{\label{fig-1} \textbf{2D polarizability as the true
    descriptor of the dielectric nature of 2D materials.}
  \textbf{a}. 3D illustration of the spatial distribution of the
  charge density change $\Delta \rho(z)$ along the z-direction for
  monolayer 2H-MoS$_{2}$ in a periodic superlattice under external
  eletric field of 0.01 V/\AA{}.  The green and red regions represent
  negative and positive induced charges, respectively. The macroscopic
  $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
  $\varepsilon_{\mathrm{SL}}^{\perp}$ are influenced by the lattice
  size $L$, while the 2D polarizabilities $\alpha^{\parallel}$ and
  $\alpha^{\perp}$ are invariant with lattice size \textbf{b}.
  $\varepsilon^{\parallel}_{\mathrm{SL}}$ (top) and
  $\alpha_{\mathrm{SL}}^{\parallel}$ (bottom) as functions of $L$ for
  the 2H TMDCs. \textbf{c}.  $\varepsilon^{\perp}_{\mathrm{SL}}$ (top)
  and $\alpha_{\mathrm{SL}}^{\perp}$ (bottom) as functions of $L$ for
  the 2H TMDCs. The polarizabilities in \textbf{b} and \textbf{c} are
  constant when $L>$15 \AA{}, compared with the $L$-dependence of
  $\varepsilon_{\mathrm{SL}}$. \textbf{d} and \textbf{e}: modeled
  $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
  $\varepsilon_{\mathrm{SL}}^{\perp}$ corresponding with \textbf{b}
  and \textbf{c}, from Eqs. \ref{eq:alpha-para-def} and
  \ref{eq:alpha-perp-def}, respectively.}
\end{figure}

% \begin{figure}[htbp]
% \centering
% \includegraphics[width=0.8\linewidth]{./img/fig2.pdf}
% \caption{\label{fig-2} The elements and 3D structures of the 2D
  % materials investigated in this study.}
% \end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=0.65\linewidth]{img/fig2_v110418.pdf}
\caption{\label{fig-3} \textbf{The universal scaling relation of the
    dielectric nature of 2D
    materials}. \textbf{a}. $\alpha^{\parallel}$, $\alpha^{\perp}$
  (bar plots) and $E_{\mathrm{g}}$ (blue dots) for all the 2D
  materials studied.  $\alpha^{\parallel}$ is observed to descend with
  increasing $E_{\mathrm{g}}$, while no apparent relation between
  $\alpha^{\perp}$ and $E_{\mathrm{g}}$ is
  observed. \textbf{b}. $(4\pi \varepsilon_{0})/\alpha^{\parallel}$
  (in \AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$, showing a linear
  correlation between each other. The energy range of visible light is
  shown in the
  background. \textbf{c}. $\alpha^{\perp}/(4\pi\varepsilon_{0})$ (in
  \AA{}) as a function of $\delta_{\mathrm{cov}}$ (definition
  schematically shown in the inset), showing a perfect linear relation
  with slope very close to $1/4\pi$. The universal scaling relation is
  also revealed using the C2DB database (squares), as superimposed on \textbf{b}
  and \textbf{c}.}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.75\linewidth]{./img/fig4.pdf}
\caption{\label{fig-4} \textbf{Transition of dielectric properties
    from 2D to 3D systems}. \textbf{a}. Scheme for the 2D-3D
  transition. $\alpha$ in the 2D material is essentially equivalent to
  $\varepsilon$ in its bulk counterpart. \textbf{b}
  $\varepsilon_{\mathrm{bulk}}^{\parallel}$ calculated from DFT
  (y-axis) compared with the predicted value from 2D
  $\alpha^{\parallel}$ (x-axis), showing good correlation. \textbf{c}
  $\varepsilon_{\mathrm{bulk}}^{\perp}$ calculated from DFT (y-axis)
  compared with the predicted value from 2D $\alpha^{\parallel}$
  (x-axis). The predicted value is in good aggreement with the DFT
  calculation when $E_{\mathrm{g}}>4$ eV, due to minimal interlayer
  coupling. The comparisons in \textbf{b} and \textbf{c} are made
  based on both HSE06 (circles) and PBE (squares) levels.}
\end{figure}
